\documentclass[sigconf]{acmart}

\settopmatter{printacmref=false} % Removes citation information below abstract
%\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
%\pagestyle{plain} % removes running headers

\usepackage{booktabs} % For formal tables
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}

% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


% DOI
%\acmDOI{10.475/123_4}

% ISBN
%\acmISBN{123-4567-24-567/08/06}

%Conference
%\acmConference[WOODSTOCK'97]{ACM Woodstock conference}{July 1997}{El
%  Paso, Texas USA} 
%\acmYear{1997}
%\copyrightyear{2016}


%\acmArticle{4}
%\acmPrice{15.00}

% These commands are optional
%\acmBooktitle{Transactions of the ACM Woodstock conference}
%\editor{Jennifer B. Sartor}
%\editor{Theo D'Hondt}
%\editor{Wolfgang De Meuter}

\graphicspath{{./figures/}}

\begin{document}
\title{Breadth First Search on FPGAs: A Pipelined Execution Approach}
%\titlenote{Produces the permission block, and
%  copyright information}
%\subtitle{Extended Abstract}
%\subtitlenote{The full version of the author's guide is available as
%  \texttt{acmart.pdf} document}


\author{     }
%\authornote{Dr.~Trovato insisted his name be first.}
%\orcid{1234-5678-9012}
\affiliation{%
  \institution{   }
%  \streetaddress{P.O. Box 1212}
%  \city{Dublin} 
%  \state{Ohio} 
%  \postcode{43017-6221}
}
\email{       }

%\author{G.K.M. Tobin}
%\authornote{The secretary disavows any knowledge of this author's actions.}
%\affiliation{%
%  \institution{Institute for Clarity in Documentation}
%  \streetaddress{P.O. Box 1212}
%  \city{Dublin} 
%  \state{Ohio} 
%  \postcode{43017-6221}
%}
%\email{webmaster@marysville-ohio.com}

% The default list of authors is too long for headers}
%\renewcommand{\shortauthors}{B. Trovato et al.}


\begin{abstract}  
    The increasing popularity of FPGAs motivates the cloud vendors to integrate FPGAs in 
    the cloud and provide FPGAs as a service. At the same time, to improve the 
    design productivity of the designers and spread the adoption of FPGAs in 
    more application domains, the vendors increasingly recommend high level 
    synthesis (HLS) tools or integrated design environments 
    to program FPGAs using C/C++ or OepnCL. However, exploring large data intensive 
    applications using high level design tools on the FPGAs for higher performance 
    remains challenging.

    In this work, we take breadth first search (BFS) on large graphs as an example 
    exploring data intensive application acceleration on the FPGAs using
    Xilinx SDAccel which is the standard design environment for Xilinx PCIe 
    based FPGAs. BFS is one of the most 
    important building blocks of graph processing and it is notoriously difficult for 
    parallel computing architectures due to the skewed data structure and irregular 
    memory access. With the high level design tools, we can rapidly identify the 
    performance bottleneck and implement corresponding optimization strategies 
    such as pipeling, prefetching, caching and buffering for the BFS. 
    According to the experiments on a set of big graphs, the optimized design 
    achieves up to 60X performance speedup compared to the baseline design. 
    Although the performance remains lower than the best handcrafted hardware 
    implementations, the HLS based design has much better software features 
    in terms of portability, ease of use and maintenance.
 
\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%

%\keywords{BFS, FPGA Cloud, High Level Synthesis, Pipelining, Caching}


\maketitle

\input{main}

\bibliographystyle{ACM-Reference-Format}
\bibliography{refs} 

\end{document}
