I would like to express profound gratitude to my supervisor in Department of Electrical and Electronic Engineering from The University of Hong Kong, Dr. Hayden Kwok-Hay So. Thank you for giving me numerous suggestions, encouragement and support for this QuickDough research project. Without his guide, this thesis would not be possible. I really appreciate the way you solve problems and the rule you do research. I believe these will be beneficial to the rest of my life.

I would like to thank Dr. Ngai Wong. Although he is not doing research exactly on reconfigurable computing, he gave me a lot of great general suggestions on doing research in the first semester of my PhD study when everything was completely new for me. He also spent quite a lot of efforts pushing me to the right track of doing research and encouraged me when I was confused. 


I want to thank the lab mates including Colin, Candice, Mingo, Ho-Cheung and Sam for all the help on my research. Most importantly, I would like to thank you for showing me the various woderful food hiding in Hong Kong. I would like to thank Sharat who gave me a lot of suggestions on the QuickDough project as well. At the same time, I want to thank the buddies including Xiachun Chen, Fang Liu, Ya Wei, Xiaoxu Shi, Big Brother Qun, Prof.Fang, Ruihua Ye and so on for climbing the hills in HK when I was extremely discouraging on my research. It was really helpful to release the stress and resume courage on my PhD study.

Finally, I would thank my family for all the support and understanding on my study in HKU. 
